### 2020-01-22 article_draft.tex
Updates from Overleaf
added more edits

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\rvv}{Z}
\newcommand{\distv}{Q}

@@

The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$, and .  Three different models are considered.  Three different models for the outcome of interest ($Y$) will be considered. Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^10 \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.   in which Sample sizes of $100$ and $200$, dimensions of $10$, $50$, 100, 150, and 200, and $\rho$ of  $0, 0.5$, or $0.8$ will be considered,

@@

% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
Above, we have used a norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This allows for creating tests and calculating p-values in a similar manner to the univariate case. 
% \textcolor{blue}{I don't understand the end of this sentence}.
However, this approach also works with more complicated functions.  For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$)
% \textcolor{blue}{(when $Z$ is sampled from what?)}
can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. An example of $\Gamma_\distv$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align*}
	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
\end{align*}
% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$

@@

To achieve this, first define $\Gamma_{1, \distv}(x), \dots, \Gamma_{p, \distv}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\distv(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\distv(x) = \max\left\{\Gamma_{1, \distv}(x), \Gamma_{2, \distv}(x), \dots, \Gamma_{p, \distv}(x)\right\}.
\end{align*}
\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gamma^*_{\distv}(\rvv))$ can still be compared to $\Gamma^*_{\distv}(\sqrt{n}\hat{\psi})$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$. This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\distv(\rvv)$ .

% Let $g_1, \dots, g_k$ be a list candiate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.  For each of the possible norms, let a p-value be defined using the following quantity:

@@

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximates with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.  Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.  Thus, the test statistic will be $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\distv}}(\hat{\rvv})$.

@@

Under local alternatives described above, 
\begin{align*}
	Pr_{\disto}\left(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha)\right) \geq \alpha
\end{align*}
Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.  Values of $\Gamma$ can be thought of as similar to $p$-valuesx

\begin{lemma} \textcolor{red}{plus $h$?}
	\begin{align*}
	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\rvv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\rvv) }(\alpha)
	\end{align*}
\end{lemma}
\textcolor{blue}{
	The proofs of these will be similar, but I am not sure quite how to do it.  While the following expansion is useful for me, I am not sure how to deal with each part:
	\begin{align*}
		Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) & = Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) - \left( Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) \right)	
	\end{align*}
	We can make arguments that the second two terms will cancel because of an assumed continuity of our function $\Gamma^*$ with respect to $Q$.  We can also think of $\Gamma^*$ as being indexed by $Q$'s covariance matrix instead of its entire distribution to make more simple continuity arguments.\\
	However, I am not exactly sure how to argue that the first two terms cancel.  Initially I want to use the continuous mapping theorem.  Because the function itself changes with $n$ and is random, I am not sure what to do.  If we again use the continuity of $\Gamma$ could we argue that the values of the random functions will be close to the values of the non-random funcitons (where $\hat\distv$ is replaced by $\distv$)\\
	My other idea was to assume that the function class of $\Gamma*$ is $P$-Donsker, but I think this may be overly complicated, and not necessary.
}

A result of \citep{anderson_integral_1955} is that for two centrally symmetric, unimodal functions, $f_1(x)$ and  $f_2(x)$, the convolution,  
\begin{align*}
	g(\theta) = \int f_1(\theta) f_2(x - \theta)
\end{align*}
is centrally symmetric and ray decreasing.  A function $f(x)$ on $\mathbb{R}^p$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.  A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex. A function $f(x)$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.

For now, we will assume that each of our $\Gamma_Q$ is a unimodal, centrally symmetric function.  In certain cases, $\Gamma_Q$ is increasing $x$ moves away from the origin. In these cases, for the purposes of this proof, instead use $\Gamma^{-1}_Q(x) = \left(\Gamma_Q(x)\right)^{-1}$.

\begin{lemma}
	\label{lemma:min_cent_sym_unm}
	Let $\Gamma_1, \dots, \Gamma_d$ all be centrally symmetric, unimodal functions.  Then $\Gamma^* = \min\left\{\Gamma_1, \dots, \Gamma_d\right\}$ is also centrally symmetric and unimodal.

	Centrally symmetric:
	\begin{align*}
	\Gamma^*(x) = \min\left\{\Gamma_1(x), \dots, \Gamma_d(x)\right\} = \min\left\{\Gamma_1(-x), \dots, \Gamma_d(-x)\right\} = \Gamma^*(-x)
	\end{align*}

	Unimodal:
	\begin{align*}
		\left\{x : \Gamma^*(x) \geq k\right\} = \left\{x : \Gamma_1(x) \geq k, \dots, \Gamma_d(x) \geq k\right\} = \bigcap_{i = 1}^d \left\{x : \Gamma_i(x) \geq k \right\}
	\end{align*}
	The intersection of multiple convex sets is also convex, so $\Gamma^*(x)$ is unimodal.
\end{lemma}

\begin{lemma}
	\label{lemma:indct_cent_sym_unm}
	Let $f(x)$ be a centrally symmetric, unimodal function.  Then $g(x) = I\left\{f(x) \geq c\right\}$ where $c \in \mathbb{R}$ is also centrally symmetric and unimodal.

	Centrally symmetric:
	\begin{align*}
	g(x) = I\left\{f(x) \geq c\right\} = I\left\{f(-x) \geq c\right\} = g(-x)
	\end{align*}

	Unimodal:
	If $k < 0$ or $k > 1$, then $\left\{x : g(x) \geq k\right\}$ will be the empty set or all of $\mathbb{R}^d$ respectively, and both sets are convex.  Otherwise, 
	\begin{align*}
		\left\{x : g(x) \geq k\right\} = \left\{x : I\left\{f(x) \geq c\right\} \geq k\right\} = \left\{x : f(x) \geq c\right\}
	\end{align*}
	which is convex by definition.
\end{lemma}
A consequence of lemmas \ref{lemma:min_cent_sym_unm} and \ref{lemma:indct_cent_sym_unm}, the function $I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\}$ is centrally symmetric and unimodal.

\begin{align*}
	\int I\left\{\Gamma^*_Q(x) \leq c_{0.95}\right\} \phi(x - \mu) dx &= \int \left(1 - I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\}\right)\phi(x - \mu) dx
	\\
	&= 1 - \int I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\} \phi(x - \mu) dx
\end{align*}
Since the subtracted quantity is decreasing by \citep{anderson_integral_1955}, the quantity as a whole will be increasing.  Thus local power is obtained.

\end{theorem}

\sh{Proof Outline: \\
\begin{itemize}
	\item Under local alternatives, $\sqrt{n}\hat{\boldsymbol{\psi}} \xrightarrow{d} N(\boldsymbol{c}, \Sigma)$
	\item With a large enough sample size, and enough MC draws, we have that for each norm: 
    \item \textcolor{blue}{Think of Gamma as a funciton indexed by $\Sigma$ to allow it to be similar.  Also make some assumptions about how smooth $\Gamma$ is with respect to this parameters. For any given value of the input ($t$) think about }
	\item \textcolor{blue}{Right now we have given up on proving things for the permutation test, but we may try to do it again at some point.} The permutation test statistic will converge in distribution to a standard normal.  This paper should help: \citep{omelka_testing_2012}
	\item For each norm selected, \citep{gupta_inequalitites_1972} states that the power will be non-decreasing as long as the rejection region is convex (This should be true most of our rejection regions), and the probability density is decreasing away from the mean (which is true of a normal distribution).  
	\item Show that for $n$ large, the norm is selected to give the best power.  Thus since each norm obtains local power, the adaptive test will also obtain local power for $n$ large.
\end{itemize}} 
\begin{align*}
	\mathcal{L}\left(\Gamma_{\hat{\distv}}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right), \Gamma_{\distv}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right)\right) \rightarrow 0
\end{align*}

>>>>

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\vmat}{\Sigma}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\rvv}{Z}
\newcommand{\distv}{Q}
\newcommand{\pf}{\Phi}
\newcommand{\gi}{\Upsilon}

@@

The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$, and .  Three different models are considered.  Three different models for the outcome of interest ($Y$) will be considered. Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.   in which Sample sizes of $100$ and $200$, dimensions of $10$, $50$, 100, 150, and 200, and $\rho$ of  $0, 0.5$, or $0.8$ will be considered,

@@

% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
Above, we have used a norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This allows for creating tests and calculating p-values in a similar manner to the univariate case. 
% \textcolor{blue}{I don't understand the end of this sentence}.
However, this approach also works with more complicated functions.  For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$)
% \textcolor{blue}{(when $Z$ is sampled from what?)}
can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. The $\distv$ used to define $\Gamma_\distv$ will always be an estimated limiting distribution and the estimators considered for this method are all asymptotically linear. Thus, $\distv$ will always be a centered multivariate normal distribution so we can index our functions through $\vmat$, the variance covariance matrix of $\distv$, instead of $\distv$ itself. An example of $\Gamma_\vmat$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align}
	\Gamma_\vmat(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv. \label{gamma:pow}
\end{align}
% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$

@@

To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
\end{align*}
\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gamma^*_{\vmat}(\rvv))$ can still be compared to $\Gamma^*_{\vmat}(\sqrt{n}\hat{\psi})$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$. This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\vmat(\rvv)$ .

% Let $g_1, \dots, g_k$ be a list candidate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.  For each of the possible norms, let a p-value be defined using the following quantity:

@@

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.  In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$. Similarly, the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ will be used in place of $\rvv$.  Thus, the test statistic will be $\Gamma_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\vmat}}(\hat{\rvv})$.

@@

Under local alternatives described above, 
\begin{align*}
	Pr_{\disto}\left(\Gamma^*_{\hat{\vmat}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\vmat}}(\hat{\rvv})}(\alpha)\right) > \alpha,
\end{align*}

Where $\hat{\rvv} \sim \hat{\distv}$ and $\rvv \sim \distv$. Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.  Values of $\Gamma$ can be thought of as similar to $p$-values.
\end{theorem}

\begin{lemma}
	\label{lemma:cont_of_gam}
	The function:
	\begin{align*}
		\Gamma_{\Sigma}(t) = Pr_\distv(||\rvv^* + t|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \sim N(0, \Sigma)
	\end{align*}
	is continuous with respect to $\Sigma$ and $t$.  
\end{lemma}

This lemma will follow because $\Gamma$ is the integral of a composition of bounded, continuous functions.

\begin{proof}
	The multivariate normal probability density function
\begin{align*}
	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)\right) 
\end{align*}	
is continuous with respect to both $\Sigma$ and $t$.

Since the exponential function, determinate, matrix inverses, and linear operators are all differentiable, they are also all continuous.  Because the multivariate normal pdf is the composition of continuous functions, it is also continuous.

It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\psi(x, \mu_n, \Sigma_n) \rightarrow \psi(x, \mu, \Sigma)$.
This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure):

\begin{align*}
	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{||x|| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{||x|| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
\end{align*}

Because the normal cdf is continuous, we know the normal quantile function will be continuous as well. Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.  These findings imply the following:

\begin{align*}
	\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x) &= Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\\
	&\leq \int_{\mathbb{R}^d} |\phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
	& = \int_{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} |\phi(t, x, \hat{\Sigma})|dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, x, \Sigma)|dt \\
	& \leq \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} \phi(t, x, \hat{\Sigma})dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, x, \Sigma)dt \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) + \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) -  \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
\end{align*}

Taking the limit as $n \to \infty$ of the quantity above, we find that the first term is zero by dominated convergence theorem.  The other four terms are also zero because of the uniform continuity of $\Phi_{\Sigma, x}$ and continuity of $\Phi^{-1}_{\Sigma, x}$
\end{proof}

\begin{lemma}
Under local alternatives, 
	\begin{align*}
		\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) 
	\end{align*}
\end{lemma}

\begin{proof}
	It was shown in Lemma \ref{lemma:cont_of_gam} that for each norm $||\cdot||$, $\Gamma_{\Sigma}(x)$ is continuous with respect to $\Sigma$ and $x$.  This finding, the continuity of the max function, and because a composition of continuous functions is also continuous it follows that

	\begin{align*}
		\Gamma^*_{\Sigma} \equiv \max\left\{\Gamma_{1, \Sigma}, \dots, \Gamma_{d, \Sigma}\right\}
	\end{align*}
	is also continuos with respect to $\Sigma$ and $x$. Under local alternatives, $\sqrt{n} \hat{\boldsymbol{\psi}} \xrightarrow{d} Z + \underline{h}$ and $\hat{\Sigma} \xrightarrow{p} \Sigma$.   It follows from the continuous mapping theorem that $\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) $
\end{proof}

It has now been establish that under local alternatives the distribution of our estimate converges to $\Gamma^*_{\Sigma}(Z + \underline{h})$.  Denote the CDF of $\Gamma^*_{\Sigma}(Z + t)$ this distribution by $F_{\Sigma, t}$ and the corresponding quantile function of the distribution by $F^{-1}_{\Sigma, t}$.

To prove unbiasedness at local alternatives, we show 
\begin{align*}
	F_{\Sigma, t}(F^{-1}_{\Sigma, 0}(1 - \alpha)) \geq F_{\Sigma, 0}(F^{-1}_{\Sigma, 0}(1 - \alpha)) = \alpha
\end{align*}
using results from the \citep{anderson_integral_1955} manuscript.
% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$

A result of \citep{anderson_integral_1955} is that for two centrally symmetric, unimodal functions, $f_1(x)$ and  $f_2(x)$, the convolution,  
\begin{align*}
	g(\theta) = \int f_1(x) f_2(x - \theta)
\end{align*}
is centrally symmetric and ray decreasing.  A function $f(x)$ on $\mathbb{R}^p$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.  A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex. A function $f(x)$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.

For now, we will assume that.  We assume that our tests will always be define our tests in such a way that we reject the null when $\Gamma^*_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}}) > c$ for some $c$. It is expected that $\Gamma^*_{\vmat}(x)$  increases as $x$ moves away from the origin. For the purposes of this proof it will be useful to define new functions

\begin{align*}
	\gi_{i, \Sigma} \equiv \left(\gi_{i, \Sigma}\right)^{-1} \text{ and } \gi_{\Sigma}^* = \min\left\{\gi_{1, \Sigma}, \dots, \gi_{d, \Sigma}\right\}
\end{align*}

that decrease as $x$ moves away from the origin.
